Estimate RSV disease burden using Hierarchical Bayesian regression

### 2023-01-26 4_RSV_disease_burden/4_RSV_disease_burden.Rmd
update

---
title: "Estimate RSV disease burden using hierarchical baysian regression"
author: "ZHE ZHENG"
date: "2023-01-26"
output: html_document
---

@@

>>>>

---
title: "Estimate RSV disease burden using Hierarchical Bayesian regression"
author: "ZHE ZHENG"
date: "2023-01-26"
output: html_document
---

@@

- Section 1: Background knowledge of estimating disease burden (hospitalizations/mortality etc) with statistical models.

- Section 2: Background knowledge of Hierarchical Bayesian regression.

- Section 3: R code for running the Hierarchical Bayesian regression to estimate in older adults by age and risk groups
